---
title: "Using the weather package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the weather package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

First, load the weather package.

```{r setup}
library(weather)
```

# Loading weather data

The weather package provides three ways of obtaining weather data.

## 1. Obtaining data from the distant past

The weather package comes with a built in dataframe called USweather. You can view this dataframe using `View()` once the package is loaded.

The dataframe contains information such as when and where the data was collected, temperature data, wind data, and precipitation data.

This dataframe contains data from many cities, so we recommend selecting just one city if you would like to perform further analysis. 

```{r}
boston <- USweather[USweather$City=="Boston", ]
```

## 2. Obtaining data from the recent past

Data can also be obtained from the website https://www.localconditions.com/ for a particular city using the `past_days()` function. This returns a dataframe containing the location, date, high and low temperature, and precipitation from approximately the past month.

```{r}
noho <- past_days("northampton", "ma", "01060")
```

## 3 Obtaining forecasted data

Forecasted data can be obtained from https://weather.com for Northampton, MA using the `weather_noho()` function. This returns a dataframe containing the location, date, wind speed, precipitation chance, and temperatures for about two weeks in the future.

```{r}
noho_forecast <- weather_noho()
```

# Creating objects of class weather_data

Data frame retrieved via any of the above methods can be converted into a weather_data class object, which holds date, location, high and low temperature, wind speed, and precipitation information, where applicable.

```{r}
boston <- weather_data(boston)
noho <- weather_data(noho)
noho_forecast <- weather_data(noho_forecast)
```

# Plotting high and low temperature data

Before you can plot high and low temperature data, you must convert the weather class into a hi_lo_temp class using the `to_hi_lo_temp()` function. 

```{r}
boston_hi_lo <- to_hi_lo_temp(boston)
noho_hi_lo <- to_hi_lo_temp(noho)
noho_forecast_hi_lo <- to_hi_lo_temp(noho_forecast)
```

Now, you can plot any of these objects using the `plot()` function.

```{r}
plot(boston_hi_lo)
plot(noho_hi_lo)
plot(noho_forecast_hi_lo)
```

# Plotting precipitation data

Before you can plot precipitation data, you must convert the weather class into a precipitation class using the `precipitation()` function. However, future forecasted data does not include precipitation in inches, so you can only plot precipitation data for past dates.

```{r}
boston_precip <- to_precipitation(boston)
noho_precip <- to_precipitation(noho)
```

Now, you can plot these objects using the `plot()` function.

```{r}
plot(boston_precip)
plot(noho_precip)
```
